\section{Publish/Subscribe}
\redtext{Enterprise Application Integration EAI:}
Order Entry
to
Order Scheduling
\&
Credit Validation
to
Order Release
to
Allocation
to 
Warehouse Management SY
to
Accounts Receivable
\bluetext{Required:}
Msg dissemination via bus;
De-coupled operation;
Dynamic evolution;
Location transparency;
Reliable message delivery;
Certified message delivery;
Fault tolerance;
Distributed event-based processing;
Event detection 
dissemination 
filtering 
correlation 
\redtext{Key of Pub/Sub:}
Many-to-many:
For comm.,
For coordination,
$M$: data sources (publishing C)
$n$: data sinks (subscribing C)
\greentext{+}
C \bluetext{decoupled},
not know each other
$\leftrightarrow$
\bluetext{tightly coupled Observer Design Pattern:}
No explicit dependencies, 
No coordination synchronization, 
Increase scalability of dis. SY,
Create highly dynamic(frequent add/remove) decentralized SY,
Decoupling in \orangetext{three dimensions:}
\greentext{Space Dec.}
No need for C (publishers \& subscribers) to hold references, C physically distributed,
\greentext{Time Dec.}
C not available same time(Event in Buffer)
\greentext{Syn. Dec.}
Control flow not blocked by interaction
\redtext{Decoupling in Diff. Interaction}
\begin{tabular}{c|c|c|c}
  \hline			
  Abstrac.&SpD&TD&SyD\\
  \hline
  MagPassingP2P&N&N& Producer\\
  PRC/RMI&N&N&Pro.\\
  Asy.PRC/RMI&N&N&Y\\
  FuturePRC/RMI&N&N&Y\\
  OberverPattern&N&N&Y\\
  TupleSpace&Y&Y&Pro.\\
  MsgQueue Pull&Y&Y&Pro.\\
  Pub/Sub&Y&Y&Y\\
  \hline
\end{tabular}
\redtext{Pub/Sub Models:}
ContentBased, 
ChannelBased(fixed, nonhierarchical), 
TopicBased(SubjectBase, hierarchical, sport news USA)
\redtext{Matching\&Filtering Content-based:}
event(Publication) $e$, 
set of subscriptions $S$, 
find all subs. $s\in S$ match $e$.
\bluetext{Subscription:}
Boolean func over predicates
\bluetext{Publication(event):}
Sets of attribute-value pairs
\\
\rtext{Two-phased Matching Algo.}
1.Match all predicates 
\bluetext{Predicate Matching Phase}
2.Match subscri. on last Phase 
\bluetext{Subscriptions Matching Phase}
\redtext{1.Predicate Mat.P.:}
set $P$ of predicates, 
event $e$, 
identify all true pred. $p$ of $P$
$\rightarrow$
\orangetext{Predicate bit vector},
Hash key: attribute name
\bluetext{General Purpose Data Structure:}
for single attr.:
4 ordered linked list(b tree) for
$=, <, >, !=$
operators,
$O(n)$ all events\&lists
\bluetext{Finite Predicate Value Domain Types:}
big matrix \greentext{eg 1000*4 for Price$\in$[1, 1000],
1000 for price, 4 for operators}, entry lookup $m[i][j]=O(1)$
\redtext{2.Subscription Mat.P.: Counting Algo}
\greentext{
S1:A<6\&B==6, S2:A<6\&B==1
$\rightarrow$
p1:A<6,p2:B==6,p3:B==1
$\rightarrow$
pred. vector:p1(S1,S2),p2(S1),p3(S2)
come Event(A,5),(B,6)
$\rightarrow$
S1 in p1,p2 matched \#=2=\#pred. of S1}
Data Structure:
pred. vector,
bit matrix.
list
\redtext{Propagation Algo:}
Match with other pred. base on Cluster.
\greentext{Same as above,
bit vector 110 for p1,p2,p3;
Cluster:S1,S2 with p1,p2,p3
but p3 not matched, delete s2}
\\
\rtext{\hlgray{Content-based Routing}}
\bluetext{\hlgray{1.Advertisements}}
\hlgray{schema or types,data sources} 
\redtext{\hlgray{Boradcast}},
\bluetext{\hlgray{2.Publications\&events}}
\hlgray{data sources}
\begin{CJK*}{UTF8}{gbsn}
\redtext{根据上一步Broker's Subscription走}
\end{CJK*},
\redtext{\hlgray{if s1 subscribers [p,>,120],[t,>,20]=[p,>,120]$\wedge$[t,>,20]}}
\bluetext{\hlgray{3.Subscriptions}}
\hlgray{query, data sinks: if empty$\{\emptyset\}\rightarrow\emptyset$}
\redtext{\hlgray{if p1 publish [p,120],[t,20] =[p,120]$\vee + $[t,20]}}
\bluetext{\hlgray{Composite Subscription:}}
\hlgray{event correlation, in network filtering,
detection of composite events}
\begin{CJK*}{UTF8}{gbsn}
\redtext{Cached 但是只能用一次, Routing Table里面不能带OR AND 必须拆开写}
\end{CJK*}
\redtext{\hlgray{Topic Based Routing:}}
\bluetext{\hlgray{Publisher:}}
\hlgray{[l1,=,business][l2,=,*][l3,=,*][n,=,*]}
\bluetext{\hlgray{Subscriber:}}
\hlgray{[l1,=,business][l2,=,market][l3,=,stocks], 
[l1,=,business]}
\bluetext{\hlgray{Publishment:}}
\hlgray{[l1,business][l2,null][l3,null][n,n1]}
