\section{RPC/SessionLayer}
\mysubsection{Remote Procedure Call:}
Call \bluetext{non-local procedure on remote S}, like local call
\textbar
\bluetext{Hidden:} 
\orangetext{Msg Def.,
content types, 
Marshalling/unmarshalling of parameters, 
Sending/Receiving Msg}
\\
\rtext{Sequence\begin{CJK*}{UTF8}{gbsn}流程\end{CJK*}, COMU}
\bluetext{1.}
C call RPC issuing req. to \redtext{C stub (a proxy obj)}. 
\bluetext{2.}
\redtext{C stub} \bluetext{encodes para.}(\orangetext{marshalling, Chap2})
\bluetext{3.}
Network Address(LAN, Internet) given, \redtext{C stub} calls the S stub via \bluetext{RPC}, 
which executed by \bluetext{RPC library, 
RPC protocol
,socket connection.}
\bluetext{4.}
\redtext{S stub} receives \bluetext{RPC.}
\bluetext{5.}
\redtext{S sub} \bluetext{decodes para.(ummarshalling)} and calls local procedure at S.
\bluetext{6.}
S executes RPC.
\bluetext{7.}
Local procedure $\overset{result}{\rightarrow}$
\redtext{S stub}
$\overset{result}{\rightarrow}$ C.
\\
\redtext{RPC Parameter}
\bluetext{CallByValue:}
easy
\bluetext{CallByRef:}
\orangetext{not work(C,S different address spaces)}
$\rightarrow$
\bluetext{CallByCopy} (serialize objects with Thrift, Protocol Buffers)
\\
\redtext{RPC Binding}
\bluetext{StaticB:}
Hardcoded reference to S; 
\btext{++:}
Simple,
Effective,
No Additional Infrastructure
\btext{--:}C S tightly coupled
\bluetext{DynamicB:}
Relies on \orangetext{Name and directory services} to locate S;
Cost in additional infrastructure, protocol, registration primitives;
$\rightarrow$
\rtext{In Sequence Above\begin{CJK*}{UTF8}{gbsn}流程\end{CJK*}}
\bluetext{Statt 3.
C requests service, 
executes RPC with S address. 
NameService provides S address
(S registed service at directory before)}
\\
\redtext{RPC with Sockets}
\rtext{In Sequence Above\begin{CJK*}{UTF8}{gbsn}流程\end{CJK*}}
\bluetext{Statt 3:
RPC call, 
P2P comm, 
C Socket(added under RPC Protocol) connect S port(S Socket and Socket). 
S accept connection.}
\\
\rtext{RPC Errors}
\bluetext{1.Lost Req.}
longer than \bluetext{Timeout of C},
C resend with \redtext{SequenceNum} $\rightarrow$ \orangetext{No Duplicates at S}
\greentext{Send fail, Resend before req. done, Resend before req. comes}
\bluetext{2.Lost Reply}
\orangetext{Same resend after Timeout}
\bluetext{S caches result, 
repeat result back} when Duplicates coming. 
If reply acknowledged, delete cache
\greentext{Reply fail, Reply longer than Timeout}
\bluetext{3.C Crash}
\orangetext{S waits ACK forever}(orphan). 
C restart using \redtext{SessionCounter}
$\rightarrow$
old reply not mix with new requests
\greentext{C Crash sofort after req., but first resp. after restart(not mix)}
\bluetext{4.S Crash}
C not Know RPC executed or not.
\redtext{S logs keeps state} of the procedure
$\rightarrow$
no Multi Executions
\greentext{state: how many \% of resp. done}
\\
\redtext{\hlgray{Failure Semantics}}
\bluetext{\hlgray{1.Maybe}}
\orangetext{\hlgray{No repeat,
One Try,
No guarantee for success}}
\btext{\hlgray{++:}}
\hlgray{Simple,
Efficient,}
\bluetext{\hlgray{2.AtLeastOnce}}
\orangetext{\hlgray{Repeat after Timeout until ACK,
No ID of duplicates}}, 
\hlgray{Acceptable for} \redtext{\hlgray{idempotent(always same result) operations, bad for non idempotent}}
\bluetext{\hlgray{3.AtMostOnce}}
\orangetext{
\begin{CJK*}{UTF8}{gbsn}Duplicate不重复处理， 不重复回复\end{CJK*}
\hlgray{
ID of duplicates: sequenceNum,} 
\redtext{\hlgray{Repeat resend, but No Repeat Execution, persistent}}, 
\hlgray{Acceptable for non-idempotent operations}, 
\redtext{\hlgray{No (or unknown)result when S crash and S not know how much he done}}
\begin{CJK*}{UTF8}{gbsn}Executed也不保存\end{CJK*}
}
\bluetext{\hlgray{4.ExactlyOnce}}
\orangetext{
\begin{CJK*}{UTF8}{gbsn}Duplicate不重复处理， 不重复回复\end{CJK*}
\hlgray{
State of procedure recorded, 
Only possible with TX
$\rightarrow$
Atomic execution, 
After S Crash and C resend(if not processed) \textbackslash S send reply (if processed), the crashed operation recovered and executed exactly once}}
\\
\redtext{Syn. Asyn. RPC}
\bluetext{Syn. RPC:}
C blocked until result from S comes
\bluetext{Asyn. RPC:}
lets C continue
\bluetext{Asyn. C:}
handle syn. to call caller th.,
Reply of RPC provided by executing \orangetext{a callback from caller th. to C} 
\redtext{or} 
\orangetext{C call polling to caller th.}.
\bluetext{Asyn. C:}
C calls redirected by S to multiple handler th.(th. pool)
\textbar \textbar \textbar
\bluetext{RPC Problems:}
not like local procedure call:
error semantics,
Reliability depends on underlying protocol (TPC),
Separate address spaces,
Lack of shared variables 
\bluetext{+}
Performance Transparency
\bluetext{+}
Scalability
\bluetext{+}
Security
\\
\mysubsection{Remote Method InvocationRMI}
\orangetext{Object-oriented} RPC;
Procedure call on remote Obj;
Method para. be \orangetext{send two ways}
(\bluetext{callByValue}$\rightarrow$Implement Serializable, 
\bluetext{callByReference}$\rightarrow$extend Remote interface);
Obj reference identifies remote Obj.
\textbar \textbar
\redtext{RPC vs RMI}
\bluetext{RPC}
Procedures of remote processes called,
Service interface provides set of procedures
\bluetext{RMI}
Obj in diff processes comm. with each other, 
Remote interface specifies methods of obj
\textbar
\redtext{RMI Protocol:}
C
$\rightarrow$
Stub(Remot Ref. Layer, Transport)
$\rightarrow$
LAN\textbackslash Internet
$\rightarrow$
Skeleton(Remot Ref. Layer, Transport, RMI Registery)
$\rightarrow$
S
\textbar
\redtext{RMI technology:}
CORBA, COM DCOM .NET,
\btext{Java RMI:}
\orangetext{Define ,extend remote interface method:}
\lstinline{import java.rmi.Remote+RemoteException;public interface Compute extends Remote{<T> T executeTask(Task<T> t)throws RemoteException;}
\orangetext{Define para.:}
\lstinline{import java.io.Serializable+math.BigDecimal;public class Pi implements Task<BigDecimal>,Serializable{private static final long serialVersionUID=227L;public BigDecimal execute(){return computePi(digits);/*]*/public static BigDecimal computePi(int digits)}
\orangetext{Implement remote obj:}
\lstinline{public class ComputeEngine implements Compute{public ComputeEngine(){super();/*]*/public <T> T executeTask(Task<T> t){return t.execute();/*]*/public static void main(String[] args){if(System.getSecurityManager()==null){System.setSecurityManager(new SecurityManager());/*]*/try{String name="Compute"; Compute engine=new ComputeEngine(); Compute stub=(C) UnicastRemoteObject.exportObject(engine,0); Registry registry=LocateRegistry.getRegistry(); registry.rebind(name,stub); print("ComputeEngine bound"); catch e}
\orangetext{Register object at S,Lookup and C call obj:}
\lstinline{public class ComputePi{public static void main(String args[]){if(System.getSecurityManager()==null){System.setSecurityManager(newSecurityManager());/*]*/try{ String name="Compute"; Registry registry=LocateRegistry.getRegistry(args[0]); Compute comp=(Compute) registry.lookup(name); Pi task=new Pi(Integer.parseInt(args[1])); BigDecimal pi=comp.executeTask(task); print(pi); catch e;}
\btext{--:}
Locked into Java,
not scale well,
Versioning problem,
Average performance,
latency insufficient
No global obj registry
\\
\redtext{\hlgray{More to Sec2. Protocol Design:}}
\lstinline{class Complex{double a,b; /*Cons.*/ public String marshal(){return concatStrings('(',valueOf(a),',',valueOf(b),')';/*]*/ public void unmarshal(String complexString){a=parseDouble(removeString(splitString(complexString,',')[0],'(')); b=parseDouble(removeString(splitString(complexString,',')[1],')'));/*]*/}
\redtext{\hlgray{M1:}}
\lstinline{class M1{Complex c1=new;Complex c2=new;String op='+';/*Cons*/ public String marshal(){return concatStrings('<',c1.marshal(),';',c2.marshal(),';',op,'>');/*]*/public void unmarshal(String m1String){c1.unmarshal(removeString(splitString(m1String,';')[0],'<')); c2.unmarshal(splitString(m1String,';')[1]); op=removeString(splitString(m1String,';')[2],'>');/*]*/}
\redtext{\hlgray{M2:}}
\bluetext{one Complex, String st='ok'.}
\redtext{\hlgray{RPC C:}}
\lstinline{class Client{/*App.Layer*/public Complex callRemoteService(Complex c1,Complex c2,String op){M1 m1=new;M2 result=sendRPC(m1);return result.cr;/*]*/ /*Repre.Layer*/public M2 sendRPC(M1 m1){String result=sendMessage(m1.marshal());M2 m2=new;return m2.unmarshal(result);/*]*/ /*SessionLayer*/public String sendMessage(String message){String ipAddress='112.32.86.113';int port=8883;Socket c=new;c.connect(ipAddress, port);c.send(message);String result=c.receive();c.close();return result;/*]*/}
\redtext{\hlgray{RPC S:}}
\lstinline{/*APPLayer*/public Complex callLocalService(Complex c1,Complex c2,String op){Complex result;switch(op){case"+":return new Complex(c1.a+c2.a,c1.b+c2.b);case"-":return new Complex(c1.a-c2.a,c1.b-c1.b);case"*":.../*]]*//*Repre.Layer*/public void processRPC(String rpc){M1 m1=new;m1.unmarshal(RPC);Complex cr=callLocalService(m1.c1,m1.c2,m1.op);M2 m2=newM2(cr,'ok');return m2.marshal();/*]*//*SessionLayer*/provideService(){int port=8888;ServerSocket ss=new;while(true){Socket c=ss.accept();String message=c.receive();result=processRPC(message);c.send(result);c.close();/*]]*/}
\hlgray{
Values never has delimiter;
If class changed, parsing the old classes fails;
Obj meta info stored into Msg$\rightarrow$XML;
Obj properties serialized in bytes, fixed length intervals$\rightarrow$Protocol Buffers
}